Certified Symbolic Finite Transducers: Formalization and Applications to String Analysis

### 2025-09-04 Paper/application.tex
change benchmark name from Rest to WebApp

\begin{table*}[h]
\centering
\small
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{1.1}
\begin{tabular}{llccccccc}
  \toprule
  \textbf{Subgroup} & \textbf{Test} & \textbf{Count} & \textbf{SAT} & \textbf{UNSAT} & \textbf{Inconclusive} & \textbf{CertiStrR (s)} & \textbf{Ostrich (s/timeout)} & \textbf{CVC5 (s/timeout)} \\
  \midrule
  \multirow{2}{*}{Replace Singleton} & Replace RE  & 94  & 77  & 16  & 1 & 0.79 & 166.27/27 & 2.67/20 \\
   & Replace Str & 323 & 103 & 211 & 9 & 1.94 & 7.10/20 & 0.81/1 \\
  \multirow{4}{*}{Replace All} & PCP & 1000 & 751 & 249 & 0 & 0.14 & 3.412/0 & unknown \\
   & RNA SAT   & 500  & 500 & 0   & 0 & 2.81 & 55.61/0 & unknown \\
   & RNA UNSAT & 500  & 0   & 500 & 0 & 3.14 & 64.185/0 & unknown \\
   & Rest      & 255  & 40  & 215 & 0 & 0.79 & 23.67/17 & 8.379/1 \\
  \bottomrule
\end{tabular}
\caption{Experimental results}
\label{tab:string_operations}
\end{table*}

>>>>

\begin{table*}[h]
\centering
\small
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{1.1}
\begin{tabular}{llccccccc}
  \toprule
  \textbf{Subgroup} & \textbf{Test} & \textbf{Count} & \textbf{SAT} & \textbf{UNSAT} & \textbf{Inconclusive} & \textbf{CertiStrR (s)} & \textbf{Ostrich (s/timeout)} & \textbf{CVC5 (s/timeout)} \\
  \midrule
  \multirow{2}{*}{Replace Singleton} & Replace RE  & 94  & 77  & 16  & 1 & 0.79 & 166.27/27 & 2.67/20 \\
   & Replace Str & 323 & 103 & 211 & 9 & 1.94 & 7.10/20 & 0.81/1 \\
  \multirow{4}{*}{Replace All} & PCP & 1000 & 751 & 249 & 0 & 0.14 & 3.412/0 & unknown \\
   & RNA SAT   & 500  & 500 & 0   & 0 & 2.81 & 55.61/0 & unknown \\
   & RNA UNSAT & 500  & 0   & 500 & 0 & 3.14 & 64.185/0 & unknown \\
   & WebApp      & 255  & 40  & 215 & 0 & 0.79 & 23.67/17 & 8.379/1 \\
  \bottomrule
\end{tabular}
\caption{Experimental results}
\label{tab:string_operations}
\end{table*}
